The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-11 src/ms.tex
caption and figure title

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.8\textwidth]{Ncommitters_vs_frac_commits.pdf}
        \caption{
            todo
        }
        \label{fig:contributor-summary:Ncommitters}
    \end{centering}
\end{figure}

>>>>

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=0.8\textwidth]{Ncommitters_vs_frac_commits.pdf}
        \caption{
            The cumulative fraction of Git commits to the \astropypkg core
            package as a function of number of contributors (committers) broken
            into three equal-length time periods between the start of \astropy
            and the feature freeze date of v5.0.
            The time eras early, mid, and recent correspond to the approximate
            year ranges 2011--2015, 2015--2018, 2018--2021 (defined more
            precisely in Section~\ref{sec:project-contributors}).
            In all eras, the majority of commits to the \astropypkg core package
            have come from a small subset of the total number of contributors.
            For example, as annotated in the figure, 90\% of the Git commits
            have come from 18, 34, and 44 committers in the early, mid, and
            recent eras, respectively.
        }
        \label{fig:contributor-summary:Ncommitters}
    \end{centering}
\end{figure}
